$\pi$ with leftovers: \\ a mechanisation in Agda

### 2021-01-20 paper/paper.tex
Get rid of unecessary subsubsections

\subsubsection{Type Safety}
Subject congruence states that applying structural congruence (\autoref{structural-congruence}) to a well-typed process preserves its well-typedness.
Subject reduction states that a well-typed process that communicates on a channel $c$ (\autoref{operational-semantics}) preserves its well-typedness and consumes $\lio$ from $c$ if $c$ is a channel in the environment.

@@

\subsubsection*{Conclusions}

@@

\subsubsection*{Future Work}
\label{replication}

>>>>

Subject congruence states that applying structural congruence (\autoref{structural-congruence}) to a well-typed process preserves its well-typedness.
Subject reduction states that a well-typed process that communicates on a channel $c$ (\autoref{operational-semantics}) preserves its well-typedness and consumes $\lio$ from $c$ if $c$ is a channel in the environment.

@@

\paragraph*{Conclusions}

@@

\paragraph*{Future Work}
